---
title: "Epi Package"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Link to shiny with leaflet example:
https://rstudio.github.io/leaflet/shiny.html 

```{r}
library(MASS)
library(epiR)
library(epitools)
library(incidence)
library(Epi)
library(epiDisplay)
library(devtools)
library(roxygen2)
library(epicalc)
library(leaflet)
library(maps)
```

```{r}
mapStates <- map("al", fill = TRUE, plot = FALSE)
leaflet(data = Fatalities) %>% addTiles() %>%
  addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)

```

```{r}
neStates <- subset(Fatalities, Fatalities$state %in% c(
  "ct","me","ma","nh","ri","vt","ny","nj","pa"
))

```



To do: 
Write function for mapping (state, city, and zip)
within the function, have it first calculate incidence/prevalence, etc. from a predefined previous function

```{r}
map_incidence<- function(m,s,t) {
  m <- fatal / pop  # insert incidence function here
  if (state == "al") {
    
  }
  t<-
    #then add mapping
}

#state variable (map)
#fatal variable (incidence) fatal/pop
#year variable (time)
```

```{r}
(table.deaths<-with(Fatalities,tapply(fatal, list(state,
year), sum)))
(table.exp<-with(Fatalities,tapply(milestot, list(state,
year), sum)))
inc.dense<-table.deaths/table.exp*100
inc.dense
plot.ts(t(inc.dense), plot.type="single") #

```


Ideas:
1.) Create a function to map incidence on state level
2.) Create a function to map incidence on based on region
3.) Create a function to map incidence nationally

#Load sample dataset available in the AER package
```{r}
library(AER)
data(Fatalities)
```