---
title: "Epi Package"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Link to shiny with leaflet example:
https://rstudio.github.io/leaflet/shiny.html 

Link to mapping examples: 
https://cran.r-project.org/web/packages/usmap/vignettes/mapping.html

Link to names of Fatalities Variables:
https://github.com/cran/AER/blob/master/man/Fatalities.Rd 

Ideas:
1.) Create a function to map incidence on state level
2.) Create a function to map incidence on based on region
3.) Create a function to map incidence nationally


```{r}
library(MASS)
library(epiR)
library(epitools)
library(incidence)
library(Epi)
library(epiDisplay)
library(devtools)
library(roxygen2)
library(epicalc)
library(maps)
library(usmap)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(rprev)
library(ggmap)
library(mapdata)
library(viridis)
```

#Load sample dataset available in the AER package
```{r}
library(AER)
data(Fatalities)
```
NOTE: no data for Alaska or Hawaii

#Cleaning the state variable data 
```{r}
us_map <- map_data("state")

tbl <- state.x77 %>%
  as_tibble(rownames = "state") %>%
  bind_cols(state_name = str_to_lower(state.abb)) %>%
  rename(value_x = Income) %>%
  select(state_name, value_x)

state_abbs <- tibble(state_full = str_to_lower(state.name), abb = str_to_lower(state.abb))
tbl_m <- left_join(tbl, state_abbs, by = c("state_name" = "abb")) %>%
  rename(id = state_full)

Fatalities_clean <- Fatalities %>%
  left_join(state_abbs, by = c("state" = "abb"))
  #right_join(us_map, by = c("state_full" = "region"))

Fatalities_clean %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `fatal`)) +
  geom_polygon(color = "white") + ggtitle("National Fatalities 1982-1988") +
  theme_void() + 
  scale_fill_viridis(name = "Fatalities (Count)") 
```
Note: must specify in the vignette that the state variable must be the full name in all lowercase and called "state_full". The function we created will merge the state_full variable with the us maps dataset.

#National Prevalence Function (Working)
```{r}
map_national_prevalence <- function(data,existing_cases,population,state,year) {
us_map <- map_data("state")
  data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population)) %>%
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state_full" = "region")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("National Prevalence of Car Fatalities 1982-1988") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
}

map_national_prevalence(Fatalities_clean,existing_cases= "fatal",population="pop", state="state_full", year="year")
```

#Mapping for Region: Northeast (Working)
```{r}
map_northeast_prevalence <- function(data,existing_cases,population,state,year) {
us_map <- map_data("state")
    data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population)) %>%
    
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state_full" = "region")) %>%
    
    filter(!! sym(state) %in% c("massachusetts","rhode island", "connecticut", "maine",
                                "vermont", "new hampshire","new york","new jersey",
                                "pennsylvania")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the Northeast") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
}

map_northeast_prevalence(Fatalities_clean,existing_cases= "fatal",population="pop", state="state_full", year="year")
```

#Mapping for Region: South (Working)
```{r}
map_south_prevalence <- function(data,existing_cases,population,state,year) {
us_map <- map_data("state")  
  data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population)) %>%
    
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state_full" = "region")) %>%
    
    filter(!! sym(state) %in% c("delaware","maryland","west virginia", "virginia", "kentucky", 
                                "tennessee","north carolina","south carolina",
                                "georgia","alabama","mississippi","arkansas",  
                                "louisiana","florida","texas","oklahoma")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the South") + 
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
}

map_south_prevalence(Fatalities_clean,existing_cases= "fatal",population="pop", state="state_full", year="year")
```

#Map for Region: Midwest (Working)
```{r}
map_midwest_prevalence <- function(data,existing_cases,population,state,year) {
us_map <- map_data("state")  
  data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population)) %>%
    
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state_full" = "region")) %>%
    
    filter(!! sym(state) %in% c("ohio","michigan", "indiana", "wisconsin", "illinois", 
                                "minnesota","iowa","missouri","north dakota",
                                "south dakota","nebraska","kansas")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the Midwest") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
}

map_midwest_prevalence(Fatalities_clean,existing_cases= "fatal",population="pop", state="state_full", year="year")
```

#Map for Region: West (Working)
```{r}
map_west_prevalence <- function(data,existing_cases,population,state,year) {
us_map <- map_data("state")  
  data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population)) %>%
    
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state_full" = "region")) %>%
    
    filter(!! sym(state) %in% c("montana","wyoming","colorado","new mexico", "arizona",       
                                "utah","california","idaho","nevada","oregon","washington",
                                "hawaii","alaska")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the West") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
}

map_west_prevalence(Fatalities_clean,existing_cases= "fatal",population="pop", state="state_full", year="year")
```
*Note: added code for Hawaii and Alaska even though the dataset we used doesn't have that data

#Region Function (Not Working: Going to Remove)
```{r}
map_region_prevalence <- function(data,existing_cases,population,state,year,geographic_region) {
us_map <- map_data("state")

  geographic_region <- data_frame(Northeast="Northeast",South="South",
                                 Midwest= "Midwest",West="West")
  
  data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population)) %>%  
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state_full" = "region")) %>%
    if (geographic_region == "Northeast") {   
filter(!! sym(state) %in% c("ma","ri","ct","me","vt","nh","ny","nj","pa")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the Northeast") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
} else if (geographic_region == "South") {
 filter(!! sym(state) %in% c("de","md","wv","va","ky","tn","nc","sc",
                                "ga","al","ms","ar","la","fl","tx","ok")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the South") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
} else if (geographic_region == "Midwest") {
    filter(!! sym(state) %in% c("oh","mi","in","wi","il","mn","ia","mo","nd","sd","ne","ks")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the Midwest") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
} else if (geographic_region == "West") {
    filter(!! sym(state) %in% c("mt","wy","co","nm","az","ut","ca", "id", "nv", "or", "wa")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("Prevalence in the West") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
} else {
   break }
}

map_region_prevalence(Fatalities_clean,existing_cases= "fatal", population="pop", state="state", year="year", geographic_region = "Northeast")
```


#Mapping for Specific Year (Not Working)
```{r}
map_national_prevalence <- function(data,existing_cases,population,state,year,specific_year) {
us_map <- map_data("state")  
  data %>%
    group_by(!! sym(state), !! sym(year)) %>%
    mutate(prevalence = !! sym(existing_cases) / !!sym(population),
           specific_year = unique(!! sym(year))) %>%
    filter(!! sym(year) == "specific_year") %>%
    
  #left_join(state_abbs, by = c("state" = "abb")) %>%
  right_join(us_map, by = c("state" = "region")) %>%
  ggplot(aes(x = long, y = lat, group = group, fill = `prevalence`)) +
  geom_polygon(color = "white") + ggtitle("National Prevalence") +
  theme_void() + 
  scale_fill_viridis(name = "Prevalence")
}

map_national_prevalence(Fatalities_clean,existing_cases="fatal",population="pop",state="state",year="year",specific_year = "1982")
```



filter(!! sym(year) == specific_year) %>%

good website: http://rdpeng.github.io/RProgDA/mapping.html 

Notes:
get ggmaps package 
check our stargazer package to generate a nice output
explain arguments 
write function to add column names to refer to the dataset variables we want (state, year, population) 
survey package in R good example
join of state name and state abbreviation and keep state abbreviation
vignette: include links and cite other things (for more further details see...)

Shiny App:
-drag by year (see changes in incidence of prevalence across years:by state or country)
-creating a reactive dataset 

-identify one state or one year: 
filter step (unique state)
filter year (unique year)
specific_state in argument
specific_year in argument


